25 years of Social Work Research

### 2015-02-25 dataCleaning.Rmd
Updated code

#load("/Users/beperron/Git/SocialWorkResearch/Data/ebscoFULL.R")
#load("/Users/beperron/Git/SocialWorkResearch/Data/proQuest.R")
#load("/Users/beperron/Git/SocialWorkResearch/Data/ebscoPsycInfo.R")

load("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/ebscoFULL.R")
load("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/proQuest.R")
load("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/ebscoPsycInfo.R")

@@

```{r}
full.df <- ebscoBWR.df
year.25 <- as.character(c(1900:1987, 2014, 2015))
years <- c("2014", "2015")
#ebsco.remove <- full.df[full.df$record %in% years, ]
ebsco.remove <- full.df[full.df$record %in% year.25, ]
ebsco.remove <- ebsco.remove[, "articleID"]
full.df <- full.df[!(full.df$articleID %in% ebsco.remove),]
```

@@

hodge <- readLines("/Users/beperron/Git/SocialWorkResearch/search_specifications/hodge.txt", n = -1)

@@

```{r}
hodge <- readLines("/Users/beperron/Git/SocialWorkResearch/search_specifications/hodge.txt", n = -1)

unique.swHistory <- filter(full.df, attributes == "journal") %>%
                distinct(record)

>>>>

load("/Users/beperron/Git/SocialWorkResearch/Data/ebscoFULL.R")
load("/Users/beperron/Git/SocialWorkResearch/Data/proQuest.R")
load("/Users/beperron/Git/SocialWorkResearch/Data/ebscoPsycInfo.R")
hodge <- readLines("/Users/beperron/Git/SocialWorkResearch/search_specifications/hodge.txt", n = -1)
#load("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/ebscoFULL.R")
#load("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/proQuest.R")
#load("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/ebscoPsycInfo.R")

@@

```{r}

year.25 <- as.character(c(1900:1987, 2014, 2015))
years <- c("2014", "2015")
#ebsco.remove <- full.df[full.df$record %in% years, ]
ebsco.remove <- full.df[full.df$record %in% year.25, ]
ebsco.remove <- ebsco.remove[, "articleID"]
full.df <- full.df[!(full.df$articleID %in% ebsco.remove),]
```

@@

@@

```{r}
unique.swHistory <- filter(full.df, attributes == "journal") %>%
                distinct(record)
